---
title: "SDS 315 HW10"
author: "Jason Lu"
output: html_document
---

## **Problem 1**

1) We are trying to assess whether or not there is an association between the number 
of FAIR policies and the racial or ethnic composition of a ZIP code.  
2) To do this, we can use the `lm()` function to create a linear regression model.
3)
```{r echo = FALSE, message = FALSE}
library(moderndive)

redline <- read.csv("redlining.csv")

redline_model <- lm(policies ~ minority + fire + age + income, data = redline)

get_regression_table(redline_model)
```
4) Because the 95% confidence interval for minority of (0.003, 0.014) *does not* include 0, there is
most likely an association between the number of FAIR policies and the 
racial/ethic composition of a ZIP code. 


## **Problem 2**

#### **Part A**
```{r echo = FALSE, message = FALSE}
library(ggplot2)
library(dplyr)

groceries <- read.csv("groceries.csv")

avg_prices <- groceries %>% 
  group_by(Store) %>% 
  summarize(AveragePrice = mean(Price))

ggplot(avg_prices) + 
  geom_bar(aes(x = Store, y = AveragePrice), stat = "identity") +
  coord_flip() + 
  labs(title = "Average Prices per Store",
       x = "Store",
       y = "Average Price")
```

#### **Part B**
```{r echo = FALSE}
product_sold <- groceries %>% 
  group_by(Product) %>% 
  summarize(store_count = n())

ggplot(product_sold) + 
  geom_bar(aes(x = Product, y = store_count), stat = "identity") + 
  coord_flip() + 
  labs(title = "Number of Stores Selling Product",
       x = "Product",
       y = "Number of Stores")
```

#### **Part C**
```{r echo = FALSE}
groceries_model <- lm(Price ~ Product + Type, data = groceries)

confint(groceries_model) %>% 
  round(2)
```
Compared with ordinary grocery stores (like Albertsons, HEB, or Krogers), 
convenience stores charge somewhere between 41 and 91 cents more for the same 
product.  

#### **Part D**
```{r echo = FALSE, message = FALSE}
library(mosaic)

store_model <- lm(Price ~ Product + Store, data = groceries)
model_coef <- coef(store_model)

sort(model_coef, decreasing = TRUE) %>% 
  head(6) %>% 
  round(2)
```
The stores charging the *highest prices* when comparing the same products are 
Whole Foods and Wheatsville Food Co-op.

#### **Part E**
```{r echo = FALSE}
model_coef %>%
  round(2)
```

The most likely outcome is that Central Market charges a similar amount to HEB 
for the same product because their estimates are very similar and their confidence 
intervals contain each other's values. When looking at other stores such as Whole 
Foods, there is a much larger difference than the difference between HEB and 
Central Market.

#### **Part F**
```{r echo = FALSE, warning = FALSE}
library(effectsize)

groceries <- groceries %>% 
  mutate(Income10K = Income / 10000)

income_model <- lm(Price ~ Product + Income10K, data = groceries)

get_regression_table(income_model)

standardize_parameters(income_model)
```
Based on the negative sign of the coefficient of Income10K, consumers in poorer 
ZIP codes seem to pay more for the same product, on average, because if you 
increase Income10K, the base price for products decreases.

A one standard-deviation increase in the income of a ZIP code seems to be 
associated with a -0.03 standard-deviation change in the price that consumers in 
that ZIP code expect to pay for the same product.