---
title: "SDS 315 Homework 2"
author: "Jason Lu (jl83734)"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
[Link to GitHub](https://github.com/jasonlu2/SDS315/blob/main/SDS_315_HW2.Rmd)

***

## **Problem 1: Beauty, or not, in the classroom**

```{r echo = FALSE, message = FALSE}
library(ggplot2)
library(dplyr)

profs <- read.csv("profs.csv")

ggplot(profs) + 
  geom_histogram(aes(x = eval), bins = 9, col = "black", fill = "white") + 
  labs(title = "Histogram of Course Evaluation Scores", 
       x = "Course Teaching Evaluation Score",
       y = "Count")
```

The distribution appears to be roughly symmetrical and unimodal with no 
significant outliers. The mean, median, and five number summary are 
`r mean(profs$eval) %>% round(1)`, `r median(profs$eval) %>% round(1)`, and 
`r fivenum(profs$eval)` respectively.

```{r echo = FALSE}
ggplot(profs) + 
  geom_boxplot(aes(x = eval, col = native)) +
  labs(title = "Boxplots of Course Evaluation Scores",
       x = "Course Teaching Evaluation Score (1-5)")
```

From the boxplots, we can see that native professors have a higher median score 
and much higher range than that of nonnative professors. However, only native 
professors appear to have outliers at the lower bounds of course evaluation scores.

This information suggests that although native English speaking professors tend 
to have a higher average course evaluation score than nonnative English speaking 
professors, there is much less variation in the individual course score of nonnative
professors compared to native professors.

```{r echo = FALSE}
ggplot(profs) + 
  geom_histogram(aes(x = eval, col = gender), fill = "white", bins = 9) +
  labs(title = "Faceted Histogram of Course Evaluation Scores",
       x = "Course Teaching Evaluation Score (1-5)",
       y = "Count") +
  facet_wrap(~gender)
```

From the two histograms, we can see the histogram of scores for male professors 
has a much larger mode than that of the female professors, and what appears to be
a higher average as well.

This means that when it comes to professors in the sample, there are more men
and those men collectively had a higher average course teaching evaluation score.

```{r echo = FALSE}
ggplot(profs) + 
  geom_point(aes(x = beauty, y = eval)) + 
  labs(title = "Scatterplot of Professors' Physical Attractiveness and Course Evaluations",
       x = "Physical Attractiveness",
       y = "Course Evaluation Score")
```

From this scatterplot, we can see truly random and scattered points and therefore,
establish that there is most likely not an association between a professor's
physical attractiveness and their course evaluation score.

## **Problem 2: bike sharing**
```{r echo = FALSE, warning = FALSE}
bikeshare <- read.csv("bikeshare.csv")

avg_rentals <- bikeshare %>% 
  group_by(hr) %>% 
  summarize(avg = mean(total))

ggplot(avg_rentals) + 
  geom_line(aes(x = hr, y = avg), size = 1) + 
  labs(title = "Average Hourly Bike Rentals",
       x = "Hour of the Day",
       y = "Average Count")
```

The line graph shows a peak at around 8 and 16 hours (8:00 AM and 4:00 PM), 
showing that most bike rentals are occuring at the beginning and end of work days.

```{r echo = FALSE, message = FALSE}
avg_rentals <- bikeshare %>% 
  group_by(hr, workingday) %>% 
  summarize(avg = mean(total)) %>% 
  mutate(workingday = ifelse(workingday == 1, "Working Day", "Non-working Day"))


ggplot(avg_rentals) + geom_line(aes(x = hr, y = avg), size = 1) + 
  labs(title = "Average Hourly Bike Rentals",
       x = "Hour of the Day",
       y = "Average Count") + 
  facet_wrap(~workingday)
```

The faceted line graphs highlight how the peaks in bike rentals mostly occur
during working days so that people can commute to work, while for non-working
days, the peak is just during the day, which may be a result of people doing 
leisurely activites.


```{r echo = FALSE, message = FALSE}
nine_hour <- bikeshare %>% 
  filter(hr == 9) %>% 
  group_by(weathersit, workingday) %>% 
  summarize(avg = mean(total)) %>% 
  mutate(workingday = ifelse(workingday == 1, "Working Day", "Non-working Day"))

ggplot(nine_hour) + 
  geom_col(aes(x = weathersit, y = avg), col = "black", fill = "white") +
  labs(title = "Average Ridership at 9 AM by Weather Situation",
       x = "Weather Situation",
       y = "Average Count") +
  facet_wrap(~workingday)
```

Here are the respective weather conditions for the numbers association with the x-axis.  
1: Clear, Few clouds, Partly cloudy, Partly cloudy  
2: Mist + Cloudy, Mist + Broken clouds, Mist + Few clouds, Mist  
3: Light Snow, Light Rain + Thunderstorm + Scattered clouds, Light Rain + Scattered clouds  

The high average count for both weather situation 1 and 2 during working days
might be correlated to the fact that people with kobs are more likely to bike to work
even if weather conditions are slightly unfavorable. Both bar graphs show a big
gap when the weather conditions are 3.

## **Problem 3: Capital Metro UT Ridership**
```{r echo = FALSE, message = FALSE}
capmetro <- read.csv("capmetro_UT.csv")

capmetro <- mutate(capmetro,
  day_of_week = factor(day_of_week,
  levels=c("Mon", "Tue", "Wed","Thu", "Fri", "Sat", "Sun")),
  month = factor(month,
  levels=c("Sep", "Oct","Nov")))

avg_boardings <- capmetro %>% 
  group_by(hour_of_day, day_of_week, month) %>% 
  summarize(avg = mean(boarding))

ggplot(avg_boardings) + 
  geom_line(aes(x = hour_of_day, y = avg, col = month)) + 
  labs(title = "Average Capital Metro Bus Boardings by Hour, Day of Week, and Month",
       x = "Hour of the Day",
       y = "Average Count") +
  facet_wrap(~day_of_week)
```

For weekdays, the hour of peak average boardings is approximately the same. However,
when it comes to weekends, there appears to be no significant peak boardings.

```{r echo = FALSE}

ggplot(capmetro) +
  geom_point(aes(x = temperature, y = boarding, col = weekend)) + 
  facet_wrap(~hour_of_day) +
  labs(title = "Scatterplot of Boardings and Temperature by Hour of Day",
       x = "Temperature",
       y = "Count of Boardings")
```

The faceted scatterplots show the amount of boardings per hour by temperature and
whether the day was a weekday or weekend. For a majority of the scatterplots, there
does not to seem to be a noticeable effect on boardings from temperature as long
as the temperature is appropriate for the time. For example when the hour is 6, 
the sun most likely isn't out, so it is colder than when the hour is 14 and the sun
is out. However, other factors, like the fact that some classes may be mandatory,
may also contribute to why temperature doesn't seem to strongly affect boardings
when hour of day and weekend status is held constant.

## **Problem 4: Wrangling the Billboard Top 100**

```{r echo = FALSE, message = FALSE}
library(kableExtra)

billboard <- read.csv("billboard.csv")

top_songs <- billboard %>% 
  group_by(performer, song) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(10)

top_songs %>% 
  kable(col.names = c("Performer", "Song", "Weeks on Billboard Top 100")) %>% 
  kable_styling()
```

The table lists 10 performers, their respective song, and how many weeks that song
was in the Billboards Top 100. 

```{r echo = FALSE}
musical_diversity <- billboard %>% 
  filter(year > 1958 & year < 2021) %>% 
  group_by(year) %>% 
  mutate(unique = n_distinct(song))

ggplot(musical_diversity) + 
  geom_line(aes(x = year, y = unique), size = 1) + 
  labs(title = "Unique Songs in Billboard Top 100 From 1959 to 2020",
       x = "Year",
       y = "Number of Unique Songs")
```

The line graph shows the number of unique songs appearing at any position on the 
Billboard Top 100 chart in any week from 1959 to 2020. Something interest to note 
is a significant decrease of unique songs from 1959 to around the 2000s by roughly 
50%, and then significant increase back to that position in an even shorter amount 
of time of 20 years compared to the approximate 40 years of decline.

```{r echo = FALSE, message = FALSE}
ten_week_hits <- billboard %>% 
  group_by(performer, song) %>% 
  summarize(weeks = n()) %>% 
  filter(weeks >= 10) %>% 
  summarize(ten_weeks = n_distinct(song))

artists <- ten_week_hits %>% 
  filter(ten_weeks >= 30)

ggplot(artists) + 
  geom_col(aes(x = reorder(performer, -ten_weeks), y = ten_weeks), col = "black", fill = "white") +
  labs(title = "Barplot of Artists with at least 30 Songs as 10-Week Hits",
       x = "Artist",
       y = "Count") +
  coord_flip()
```

The bar plot displays the 19 musical artists who have had at least 30 songs in 
the Billboard Top 100 for a minimum of 10 weeks. The artists arae listed in 
ascending order of least songs to most songs, starting of course from 
`r min(artists$ten_weeks)` and ending at `r max(artists$ten_weeks)`.
