---
title: "SDS 315 Homework 3"
author: "Jason Lu"
output: html_document
---

***

## **Problem 1:**

```{r echo = FALSE, message = FALSE}
library(dplyr)

creatinine <- read.csv("creatinine.csv")

lm(creatclear ~ age, data = creatinine) %>% coef()

creatinine_model <- lm(creatclear ~ age, data = creatinine) %>% 
  summary()

creatinine_intercept <- creatinine_model$coefficients[1, 1]
creatinine_slope <- creatinine_model$coefficients[2, 1]
```

Given the intercept and slope, we can determine an expected creatinine clearance
rate for a 55 year-old. Using the formula y = mx+b, with m being the slope
(`r creatinine_slope %>% round(2)`), x being the age (55), and b being the y-intercept
(`r creatinine_intercept %>%  round(2)`), we calculate an expected creatinine clearance of
`r (55*creatinine_slope + creatinine_intercept) %>%  round(2)` mL per minute.

The slope, m, means that for every increase in age by one year, the creatinine 
clearance level is supposed to decrease by 
`r creatinine_slope %>% round(2) %>% abs()` mL per minute.

Using the same equation, the expected creatinine clearance rate for a 40 year old
and 60 year old are `r (40*creatinine_slope + creatinine_intercept) %>%  round(2)` 
and `r (60*creatinine_slope + creatinine_intercept) %>%  round(2)` respectively.
To find the residual value, we do actual value minus expected value, to find that
the 40 year old's creatinine clearance of 135 mL/min is higher than what is expected
and in conclusion, healthier than the 60 year old with a rate of 112 mL/min.

## **Problem 2**
```{r echo = FALSE, message = FALSE}
library(tidyverse)
library(kableExtra)

marketmodel <- read.csv("marketmodel.csv")

stock_list <- c("AAPL", "GOOG", "MRK", "JNJ", "WMT", "TGT")

# initialize data frame
results <- data.frame(
  Ticker = character(),
  Intercept = numeric(),
  Slope = numeric(),
  R_Squared = numeric()
)

# loop through stock_list to fill data frame
for (name in stock_list) {
  stock <- lm(formula = paste(name, "~ SPY"), data = marketmodel)
  
  intercept <- coef(stock)[1]
  slope <- coef(stock)[2]
  r_squared <- summary(stock)$r.squared
  
  results <- bind_rows(results, data.frame(
    Ticker = toupper(name),
    Intercept = intercept,
    Slope = slope,
    R_Squared = r_squared
  ))
}
```
From the video, the $\beta$ of a stock is measuring the change as a percent in 
an asset's return given a 1% change in the market portfolio and is a measure of 
systematic risk for a firm's stock. Firms with less systematic risk will have a 
$\beta$ value less than 1 and firms with a higher systematic risk will have a 
$\beta$ value greater than 1. For example, a grocery store is like to have a 
$\beta$ value less than 1 because groceries are an inelastic good, while a
jewelery store would like have a $\beta$ value greater than 1, since jewelry
is a luxury good. By default, the system risk of a firm is 1 and a $\beta$ value 
of 0 indicates no systematic risk. There is a rare case where $\beta$ can be 
negative, and this just means that a firm would do very well when the market portfolio
does poorly, and acts as an form of "insurance" in the event of a market downturn.

```{r echo = FALSE}
# create table with kableExtra
results %>% 
  kable(col.names = c("Stock", "Intercept", "Slope", "R-Squared"), row.names = FALSE) %>% 
  kable_styling()
```

The table displays 6 stocks and their respective variables. These variables include
$\beta_0$ (intercept), $\beta_1$ (slope), and R^2^ for each regression of the 
corresponding stock.

```{r echo = FALSE}
max_result <- results[results$Slope == max(results$Slope), ]
min_result <- results[results$Slope == min(results$Slope), ]
```
From the table, the stock with the *lowest* systematic risk is `r min_result$Ticker` 
and the stock with the *highest* systematic risk is `r max_result$Ticker`.

## **Problem 3**
```{r echo = FALSE}
covid <- read.csv("covid.csv")

italy <- covid %>% 
  filter(country == "Italy")
spain <- covid %>%
  filter(country == "Spain")

italy_model <- lm(log(deaths) ~ days_since_first_death, data = italy)
spain_model <- lm(log(deaths) ~ days_since_first_death, data = spain)

italy_growth_rate <- coef(italy_model)[2] * 100
italy_doubling_time <- (70 / italy_growth_rate) %>% 
  round()

spain_growth_rate <- coef(spain_model)[2] * 100
spain_doubling_time <- (70 / spain_growth_rate) %>% 
  round()
```
The estimated growth rate and doubling time for Italy are 
`r italy_growth_rate %>% round(3)`% per year and `r italy_doubling_time %>%  round()` 
days respectively.

The estimated growth rate and doubling time for Spain are 
`r spain_growth_rate %>%  round(3)`% per year and `r spain_doubling_time %>%  round()` 
days respectively.

```{r echo = FALSE}
ggplot(covid) + geom_line(aes(x = days_since_first_death, y = deaths, col = country)) +
  labs(title = "Daily Covid Deaths Over Time in Italy and Spain",
       x = "Days Since First Death",
       y = "Number of Deaths")
```

## **Problem 4**
```{r echo = FALSE}
milk <- read.csv("milk.csv")

milk_model <- lm(log(sales) ~ log(price), data = milk)
beta <- coef(milk_model)[2]
```

Since the economists' power-law model is an exponential function, we just take the
logarithm of both sides to fit the model. After doing this, we get that the
estimated price elasticity of demand for milk,($\beta$), is equal to 
`r beta %>% round(3)`.












