---
title: "SDS 315 Homework 5"
author: "Jason Lu"
output: html_document
---

***

## **Problem 1**

```{r echo = FALSE, message = FALSE}
library(ggplot2)
library(mosaic)

set.seed(123)
sec_sim <- do(100000) * nflip(2021, prob = .024)

sec_p_value <- sum(sec_sim >= 70) / 100000
```

In this problem, the null hypothesis is that securities trades from the Iron Bank 
are flagged at the same 2.4% baseline rate as that of other traders.  

The test statistic is the proportion of flagged trades to total trades.  

```{r echo = FALSE}
ggplot(sec_sim) + geom_histogram(aes(x = nflip), binwidth = 1)
```

The calculated p-value is `r sec_p_value`.  

Because the p-value is quite smaller than 0.05, it suggests that the proportion
of flagged trades happening at Iron Bank is much higher than the baseline rate, 
and therefore, the SEC most likely needs to conduct an investigation to make sure
that this was just by chance, or there is an explanation behind the small p-value.

## **Problem 2**
```{r echo = FALSE}
health_sim <- do(100000) * nflip(50, prob = .03)

health_p_value <- sum(health_sim >= 8) / 100000
```

In this problem, the null hypothesis is that restaurants, including Gourmet Bites, 
in the city are cited for health code violations at the same 3% baseline rate.  

The test statistic is the proportion of health code violations to all restaurant 
inspections.  

```{r echo = FALSE}
ggplot(health_sim) + geom_histogram(aes(x = nflip), binwidth = 1)
```

The calculated p-value is `r health_p_value`. 

Because the p-value is significantly smaller than 0.05, it suggests that the proportion
of health code violations occurring at Gourmet Bites restaurants is much higher than 
the baseline rate, and that the Health Department should follow through with their
plan to take appropriate action.

## **Problem 3**
```{r echo = FALSE, message = FALSE}
# Part A
library(tidyverse)

text <- readLines("brown_sentences.txt")
text.df <- data.frame(sentence = text)
letter_freq <- read.csv("letter_frequencies.csv")

calculate_chi_squared = function(sentence, freq_table) {
  
  # Ensure letter frequencies are normalized and sum to 1
  freq_table$Probability = freq_table$Probability / sum(freq_table$Probability)
  
  # Remove non-letters and convert to uppercase
  clean_sentence = gsub("[^A-Za-z]", "", sentence)
  clean_sentence = toupper(clean_sentence)
  
  # Count the occurrences of each letter in the sentence
  observed_counts = table(factor(strsplit(clean_sentence, "")[[1]], levels = freq_table$Letter))
  
  # Calculate expected counts
  total_letters = sum(observed_counts)
  expected_counts = total_letters * freq_table$Probability
  
  # Chi-squared statistic
  chi_squared_stat = sum((observed_counts - expected_counts)^2 / expected_counts)
  
  return(chi_squared_stat)
}

brown_sentences_chi_squared <- sapply(text.df$sentence, calculate_chi_squared, letter_freq)

ggplot(data.frame(brown_sentences_chi_squared))  +
  geom_histogram(aes(x = brown_sentences_chi_squared), binwidth = 5)
```

```{r echo = FALSE, message = FALSE}
# Part B
library(kableExtra)

sentences <- c(
    "She opened the book and started to read the first chapter, eagerly anticipating what might come next.",
    "Despite the heavy rain, they decided to go for a long walk in the park, crossing the main avenue by the fountain in the center.",
    "The museum’s new exhibit features ancient artifacts from various civilizations around the world.",
    "He carefully examined the document, looking for any clues that might help solve the mystery.",
    "The students gathered in the auditorium to listen to the guest speaker’s inspiring lecture.",
    "Feeling vexed after an arduous and zany day at work, she hoped for a peaceful and quiet evening at home, cozying up after a quick dinner with some TV, or maybe a book on her upcoming visit to Auckland.",
    "The chef demonstrated how to prepare a delicious meal using only locally sourced ingredients, focusing mainly on some excellent dinner recipes from Spain.",
    "They watched the sunset from the hilltop, marveling at the beautiful array of colors in the sky.",
    "The committee reviewed the proposal and provided many points of useful feedback to improve the project’s effectiveness.",
    "Despite the challenges faced during the project, the team worked tirelessly to ensure its successful completion, resulting in a product that exceeded everyone’s expectations."
)

sentence_df <- data.frame(sentence = sentences)

sentences_chi_squared <- sapply(sentence_df$sentence, calculate_chi_squared, letter_freq)

p_values <- 1 - pchisq(sentences_chi_squared, df = mean(brown_sentences_chi_squared))

p_values_df <- data.frame(sentence = sentences, p_value = p_values %>% round(3))
watermarked <- p_values_df[which.min(p_values), ]
p_values_df <- data.frame(p_value = p_values %>% round(3))

p_values_df %>% 
  kable(col.names = c("Sentence", "p-value")) %>% 
  kable_styling()
```

Given the extremely low p-value for the sentence, which when rounded to three 
decimal points becomes 0, the sentence produced by an LLM with a watermark is 
"`r watermarked$sentence`"
