---
title: "HW 9"
author: "Jason Lu"
output: html_document
---

***

## **Problem 1**

#### **Part A**

```{r echo = FALSE, message = FALSE}
library(dplyr)

turnout <- read.csv("turnout.csv")

# Proportion of those receiving a GOTV call who voted in 1998
gotv_prop_yes <- mean(turnout$voted1998[turnout$GOTV_call == 1])

# Proportion of those not receiving a GOTV call who voted in 1998
gotv_prop_no <- mean(turnout$voted1998[turnout$GOTV_call == 0])


# 95% confidence interval for the difference in the two proportions
call_yes_count <- sum(turnout$GOTV_call == 1)
call_no_count <- sum(turnout$GOTV_call == 0)

margin_of_error <- 1.96 * sqrt((gotv_prop_yes * (1-gotv_prop_yes) / call_yes_count) + 
                                 (gotv_prop_no * (1-gotv_prop_no) / call_no_count))

lower_bound = gotv_prop_yes - gotv_prop_no - margin_of_error
upper_bound = gotv_prop_yes - gotv_prop_no + margin_of_error
```

The proportion of those receiving a GOTV call who voted in 1998 is 
`r gotv_prop_yes %>% round(3)`.  
The proportion of those *not* receiving a GOTV call who voted in 1998 is 
`r gotv_prop_no %>% round(3)`.
We are 95% confident that the interval for the difference in proportions is 
`r lower_bound %>%  round(3)`, `r upper_bound %>%  round(3)`.  

#### **Part B**

```{r echo = FALSE, message = FALSE}
summary_stats <- aggregate(cbind(voted1996, AGE, MAJORPTY) ~ GOTV_call, 
                           data = turnout, FUN = mean)

summary_stats
```

#### **Part C**
```{r echo = FALSE}
library(MatchIt)

# Check "matched" data set is balanced 
turnout_matched <- matchit(GOTV_call ~ voted1996 + AGE + MAJORPTY, 
                           data = turnout, ratio = 5) %>% 
  match.data

matched_summary_stats <- aggregate(cbind(voted1996, AGE, MAJORPTY) ~ GOTV_call, 
                           data = turnout_matched, FUN = mean)

# Repeat analysis from Part A with matched data
gotv_matched_prop_yes <- mean(turnout_matched$voted1998[turnout_matched$GOTV_call == 1])
gotv_matched_prop_no <- mean(turnout_matched$voted1998[turnout_matched$GOTV_call == 0])

call_matched_yes_count <- sum(turnout_matched$GOTV_call == 1)
call_matched_no_count <- sum(turnout_matched$GOTV_call == 0)

matched_margin_of_error <- 1.96 * sqrt((gotv_matched_prop_yes * (1-gotv_matched_prop_yes) / call_matched_yes_count) + 
                                 (gotv_matched_prop_no * (1-gotv_matched_prop_no) / call_matched_no_count))

matched_lower_bound = gotv_matched_prop_yes - gotv_matched_prop_no - matched_margin_of_error
matched_upper_bound = gotv_matched_prop_yes - gotv_matched_prop_no + matched_margin_of_error
```

The proportion of those receiving a GOTV call in the matched data set who voted in 1998 is 
`r gotv_matched_prop_yes %>% round(3)`.  
The proportion of those *not* receiving a GOTV call in the matched data set who voted in 1998 is 
`r gotv_matched_prop_no %>% round(3)`.
We are 95% confident that the interval for the difference in proportions in the matched data set is 
`r matched_lower_bound %>%  round(3)`, `r matched_upper_bound %>%  round(3)`.  

Since the confidence interval after matching the data does not conclude zero, we 
can conclude that the GOTV call did increase the likelihood of voting in the 
1998 election.  

## **Problem 2**

#### **Part A**
```{r echo = FALSE}
library(ggplot2)

solder <- read.csv("solder.csv")

# Boxplots
ggplot(solder) + geom_boxplot(aes(x = Opening, y = skips)) +
  labs(title="Solder Skips by Opening Size of Solder Gun",
       x="Opening Size", y="Number of Skips")

ggplot(solder) + geom_boxplot(aes(x = Solder, y = skips)) +
  labs(title="Solder Skips by Solder Thickness of Alloy Used",
       x="Solder Thickness", y="Number of Skips")
```

#### **Part B**
```{r echo = FALSE}
library(moderndive)

# Regression model
model <- lm(skips ~ Opening + Solder + Opening:Solder, data = solder)

# Table for each coefficient in model
get_regression_table(model)
```

#### **Part C**
The baseline solder skips on the circuit board for solder guns with a large opening 
and thick alloy is 0.393.  
The main effect for the `OpeningM` variable is 2.407 skips. This is the effect of 
`OpeningM` in isolation.  
The main effect for the `OpeningS` variable is 5.127 skips. This is the effect of 
`OpeningS` in isolation.  
The main effect for the `SolderThin` variable is 2.280 skips. This is the effect of 
`SolderThin` in isolation.  

The interaction effect for `OpeningM` and `SolderThin` is -0.740 solder skips. 
In other words, circuit boards with solder guns with a medium opening and thin alloy 
yield 0.740 less skips than what you would expect from summing the individual 
“isolated” effects of the two variables.  

The interaction effect for `OpeningS` and `SolderThin` is 9.653 solder skips. 
In other words, circuit boards with solder guns with a small opening and thin alloy 
yield 9.653 more skips than what you would expect from summing the individual 
“isolated” effects of the two variables.  

A large opening paired with thick alloy should be recommended because that combination 
produces the least skips from the following calculations:  

Large Opening, Thick Alloy (Baseline) = 0.393

Medium Opening, Thick Alloy:
0.393 + 2.407 = 2.800

Small Opening, Thick Alloy:
0.393 + 5.127 = 5.520

Large Opening, Thin Alloy:
0.393 + 2.280 = 2.673

Medium Opening, Thin Alloy:
0.393 + 2.407 + 2.280 - 0.740 = 4.340

Small Opening, Thin Alloy:
0.393 + 5.127 + 2.280 + 9.653 = 17.453





